---
title: "Lab1Part2"
author: "Annika Kufrovich"
date: "February 7, 2018"
output: html_document
---

#Genetic Diversity
*This datset contains genetic diverity for different populations and compares it to the distance from East Africa*.

```{r, echo=FALSE}
library(Lock5Data)
library(rmarkdown)
data("GeneticDiversity")
knitr::kable (GeneticDiversity,caption ="GeneticDiversity",padding =0)
```

```{r, echo=FALSE, results='asis'}
stargazer::stargazer(GeneticDiversity, type="html",title= "GeneticDiversity")
```

Based on the data we can conclude that the average genetic diversity is *`r mean(GeneticDiversity$GeneticDiversity)`* with a standard deviation of *`r sd(GeneticDiversity$GeneticDiversity)`*.

##Five Most Genetically Diverse Populations Worldwide
This table depicts the five most genetically diverse countries worldwide from the dataset Genetic Diversity wi thin the lock5data package

1. **BiakaPygmy**
    + Genetic Diversity: `r sort(GeneticDiversity$GeneticDiversity, TRUE)[1]`
    + Distance: `r sort(GeneticDiversity$Distance, TRUE)[1]`
2. **Yoruba**
    + Genetic Diversity: `r sort(GeneticDiversity$GeneticDiversity, TRUE)[2]`
    + Distance: `r sort(GeneticDiversity$Distance, TRUE)[2]`
3. **Mandenka**
    + Genetic Diversity: `r sort(GeneticDiversity$GeneticDiversity, TRUE)[3]`
    + Distance: `r sort(GeneticDiversity$Distance, TRUE)[3]`
4. **Paestinian**
    + Genetic Diversity: `r sort(GeneticDiversity$GeneticDiversity, TRUE)[4]`
    + Distance: `r sort(GeneticDiversity$Distance, TRUE)[4]`
5. **Makrani**
    + Genetic Diversity: `r sort(GeneticDiversity$GeneticDiversity, TRUE)[5]`
    + Distance: `r sort(GeneticDiversity$Distance, TRUE)[5]`

```{r, echo=FALSE}
summary(GeneticDiversity)
```

##Five Number Summaries
Genetic Diverstiy: (`r quantile(GeneticDiversity$GeneticDiversity)`)  

Distance from East Africa: (`r quantile(GeneticDiversity$Distance)`)

    
